Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-14 lloveras_2020_Albert_Section4.tex

@@

\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper. Nothing not needed to read this paper is provided. Also, no derivation of equations are provided. References are given so that the reader can dig deeper if so desires. Points to cover are:
\begin{itemize}
  \item Selected targets, instruments used. One paragraph.
  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
  \item What is FBE, what is LDEM, what is R. Why we care about these three quantities and what is their physical meaning should be clear. Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
\end{itemize}
}

To perform the comparison two specific rotations were selected, CR-2082 (2009, 05 April through 03 May), a deep minimum period between solar cycles (SCs) 23 and 24 characterized by virtually no ARs, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24.

To determine the thermodynamical structure of both rotations, the DEMT technique was applied to respective time series of EUV images covering each first half rotation. To study CR-2082 and CR-2208 data taken by the EUVI-B/STEREO and AIA/SDO instruments was used, respectively.

In DEMT, the low corona in the height range $1.0$ to $1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic cell (or voxel) is set to 0.01 \rsun \ in the radial direction, while is set 2\deg\ in both the latitudinal and longitudinal directions. We carried out a reconstruction using half of a solar rotation blocking the lines-of-sight comming from the disk (i.e. only using off-limb data).

Using the high cadence of data available, one image every 10 minutes were used. The selected images were averaged in 6-hour intervals which, given the angular resolution, is the cadence needed to fully constrain the inversion problem, for a total of about 55 images to cover a half solar rotation. For both rotations, the first 14 days of data were used.

EUV images are affected by instrumental stray light contamination, which can be corrected by deconvolution of the point spread function (PSF). While in the case of AIA images there is no reliable determination of its PSF, it has been well determined for EUVI-B by \citet{shearer_2012}. For this article, all EUVI images were stray-light corrected. For the details of impact in $\Nm$ and $\Tm$, refer to \citet{lloveras_ba2017}.

\diego{
Unlike in previous works, a 3D regularization scheme was applied, thus spurious artifacts (nduced by the previous longitude latitude regularization schemei) were minimized in the first two heights of the tomographic grid.}

We refer the reader to \citet{frazin_2009} for a detailed description of the technique, and to \citet{vasquez_2016} for a recent review on all published work based on it. Here we summarize the key points. The technique involves two consecutive procedures.

In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently. As a result, the 3D distribution of the so called {filter band emissivity} (FBE) is determined for each band separately. The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel. Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series. To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all pairs of synthetic and real images is minimized. Spatial regularization terms are also included in the objective function as to minimize high frequency spurious artifacts that are due to the specific characteristics of the SRT sparse projection matrix \citep{frazin_2009,frazin_2000}. {Due to optical depth issues that may affect LOSs} passing very close to the limb, and to the decay of intensity with radii, the 3D maps produced by DEMT analysis typically cover the height range 1.02 to 1.23 \rsun \ \citep{frazin_2009}.

\diego{COMO INTRODUZCO EL NIVEL DE REGULARIZACION? For each instrument, the DEMT analysis involves a cross-validation study to determine the optimal level of regularization.}

{In a second step, the FBE values obtained for all bands in each voxel are used to constrain the determination of a {local differential emission measure} (LDEM) distribution, which describes the temperature distribution of the electron plasma contained in each individual tomographic grid voxel. Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}

@@

{
Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.
}

Once the LDEM is determined at each voxel, the average squared electron density $\langle \Ne^2 \rangle$ and the electron mean temperature $\Tm$ in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,

@@

being the average relative difference between the tomographic and the synthetic FBEs. The final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}

@@

{For analysis purposes, the geometry of all traced magnetic field lines is classified. They are first classified as open or closed according to their full geometry. Each closed magnetic field line is further classified as ``small" or ``large", according to its coronal length $L$ being smaller or larger than the median value ${\rm Md}(L)$ of the whole population, respectively. This median value is \diego{${\rm Md}(L)=0.50$} and $0.46\,\mrsun$ for CR-2082 and CR-2208, respectively. Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e. their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).} \notebyalbert{Diego, aquí ordené y corregí mucho y creo que es un buen ejemplo de corrección de estilo de redacción, si querés comparar con como estaba antes. Nota: MHD no tiene source surface! Ahora bien, además informo ${\rm Md}(L)$. Para ello multipliqué por dos el valor mediano de las longitudes de las piernas (que recuerdo de memoria, por ahí la pifié). Vale la pena que le muestres estos histogramas a Fede y la pieza de código de donde sale, para confirmar la metodología y de paso los números. Es importante.}

At this stage, all DEMT and AWSoM products, electron density and {temperature} in particular, can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell {is obtained. This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

@@

\notebyalbert{Este párrafo debe ser movido al menos aquí (estaba más abajo), pues el siguiente párrafo ya utiliza el concepto up/down. Además está corregido.} {Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\notebyalbert{Reordené y corregí mucho el siguiente párrafo. Lo que see lee es correcto en cada detalle y palabra? Está bien explicado todo lo que concierne a chi-suqared? La jerga estadística es precisa y correcta (no confundir confidence level con confidence interval, está bien?}
{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$. \diego{hablemos sobre esta frase} We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level. In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis. Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. Both fits consider tomographic systematic uncertainty of the electron temeprature and density, respectively estimated to be $\Delta(\Tm) \approx 0.07\,\MK$ and $\Delta(N_e)\approx 4.0\times 10^6\,\cm^{-3}$ by \citet{lloveras_2017}. \notebyalbert{No comprendo bien si esta última linea está bien ubicada aquí, de todas formas lo corregí un poco. Precisaría que discutamos los tres estos tres párrafos en naranja el lunes.} In summary, to be selected a leg must meet all three following conditions:}

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The condifence level of both the exponential and linear fits must be larger than 90\%.} \notebyalbert{Aquí corregí, está bien expresado?}\diego{si!}
\end{enumerate}

{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:} \notebyalbert{Simplifiqué mucho esto.}

@@

In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the 48000 legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the 57000 legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III. \notebyalbert{Luego de des-ralear, las piernas seleccionadas en Figura 4 eran del orden de 100 mil, para  ambas rotaciones. Algo no está consistente aquí.}\diego{Statloop 6 alturas noda algo asi como 150k piernas, algunas no se trazan (entre 30 y 40k) lo cual nos deja aprox 110k. SUpongo que te quedaste con ese numero. Pero elimino los cuasi isotermicos, perdemos 30k en el streamer y 10k en CH. Luego hacemos una seleccion qie involucra footpoints y ahi perdemos lo que falta! Es decir, el numero del draft ya es des-raleado.}

@@

In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\lesssim 5\%$ and $\approx 2\%$ for the electron temperature and density, respectively. \notebyalbert{son estos errores compatibles con los informados en la Sección 2?}

>>>>

\albert{Based on time-series of EUV images, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM) of the solar corona. The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. In DEMT, the low corona in the height range $1.0-1.25\,\mrsun$ is discretized in a spherical computational grid. The size of the tomographic cell (or voxel) is typically set to 0.01 \rsun \ in the radial direction and 2\deg\ in both the latitudinal and longitudinal directions. The cadence of the data time-series is set to 6\,hr. The main product of the technique is the local DEM (LDEM), a measure of the temperature distribution of the plasma contained in each voxel of the tomographic grid. A recent review by \citet{vasquez_2016} summarizes the DEMT works up until then. More recently \citet{lloveras_2017} applied DEMT to study the last two solar minima, and \citet{maccormack_2017} developed a new DEMT product concerning the energetics of the inner solar corona.}

@@

%\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper. Nothing not needed to read this paper is provided. Also, no derivation of equations are provided. References are given so that the reader can dig deeper if so desires. Points to cover are:
%\begin{itemize}
%  \item Selected targets, instruments used. One paragraph.
%  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used %for their processing. One paragraph.
%  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
%  \item What is FBE, what is LDEM, what is R. Why we care about these three quantities and what is their physical meaning should be clear. Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
%\end{itemize}
%}

\albert{We carried out the 3D DEMT reconstruction and MHD modeling of two target Carrington rotations (CR). We selected CR-2082 (2009, 05 April through 03 May), a deep minimum rotation between solar cycles (SC) 23 and 24, and CR-2208 (2018, 02 September through 29 September), a rotation during the early declining fase of SC 24. To study CR-2082 and CR-2208 data taken by the STEREO/EUVI-B/STEREO and SDO/AIA instruments was used, respectively. The EUVI and AIA data were prepared using the latest processing tools and calibration corrections provided by their teams through the SolarSoft package. For this work, we introduced two improvements in the implementation of the DEMT technique, as described next.}

\albert{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we opted to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Fistly, the fast dynamics that typically characterizes those structures is abscent from the data. Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, coronal dynamics induced artifacts are reduced compared to previous DEMT reconstructions.}
.
\albert{The solution of the tomographic problem involves a very large sparse matrix. Such type of inversion problems are characterized by spurious high-frequency artifacts in the solution, which can be mitigated through \emph{regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions.}

\albert{We summarize next the main aspects of DEMT required for the analysis of this work. We refer the reader to \citet{frazin_2009} for a full description of the technique.}

In a first step, the time series of EUV images is used to solve a solar rotational tomography (SRT) problem, for each EUV band independently. As a result, the 3D distribution of the so called \emph{filter band emissivity} (FBE) is determined for each band separately. The FBE, {an emissivity-type quantity}, is defined as the wavelength integral of the coronal EUV spectral emissivity and the telescope's passband function of each EUV channel. Line-of-sight (LOS) integration of the FBE provides synthetic images that can be quantitatively compared to the real data in the time series. To find the FBE, the tomographic problem is posed a global optimization problem in which the quadratic norm of the difference between all \albert{pairs of synthetic and real images is minimized.}

{In a second step, the FBE values obtained for all bands in each voxel \albert{of the tomographic grid are used to constrain the determination of the LDEM which, as described in Section \ref{intro}, describes the temperature distribution of the plasma within the individual voxel.} Specifically, at each tomographic voxel $i$, the FBE of the band $k$ is related to the LDEM of the voxel according to}

@@

\noindent
\albert{where $K$ is the number EUV bands, and $\TRF^{(k)}$ is the \emph{temperature response function} of the $j$-th detector. The TRFs are here computed based on the (known) channel’s passband times the coronal emissivity at that temperature (normalized by the squared electron density). The emissivity model used here is provided by the latest version of the CHIANTI atomic database and plasma emission model \citep{delzanna_2015,landi_2013}.}

Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. These non-reconstructed voxels are indicated as black voxels in the Carrington maps of the reconstructed DEMT reults in Section \ref{resu}.

Once the LDEM is determined at each voxel, \albert{the LDEM-averaged squared electron density $\Nm^2$ and electron temperature $\Tm$} in the voxel can be computed by taking its zeroth and first moments over temperature. More specifically, at the $i$-th voxel,

@@

\noindent 
\albert{being the} average relative difference between the tomographic and the synthetic FBEs. The final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
%\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}

@@

{For analysis purposes, \albert{the traced magnetic field lines are classified as open or closed according to their full geometry. Each closed field} line is further classified as ``small" or ``large", according to its coronal length $L$ being \albert{respectively smaller or larger than the median value of the whole population, which is ${\rm Md}(L)\approx 0.5\,\mrsun$ for both rotations.} Finally, each closed magnetic field line is separated in its two ``legs", defined as the two segments that go from each of its two footpoints (i.e. their location at $r=1\,\mrsun$) to its apex (i.e., the location of maximum height).}

At this \albert{stage, DEMT and AWSoM products} can be traced along open and closed magnetic field lines. Once the field line geometry is computed in high spatial resolution, only one sample point per tomographic cell is kept (the median one). To each sample point, the results corresponding to the tomographic voxel where it is located are assigned to it. As a result, for each field line one data point per tomographic cell {is obtained. This approach} was firstly used by \citet{huang_2012} to {study temperature} structures in the solar minimum {corona and by} \citet{nuevo_2013} to expand that analysis to rotations with different level of activity.

@@

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and considering time-averaged heating rates.}

\noindent\notebyalbert{El párrafo que sigue describe un algoritmo para identificar y seleccionar piernas up/down. Es correcta la jerga de "confidence level'' y el como se describe chi-squared test? Están bien mencionadas ambas cosas? Por ejemplo: confidence-level y conficence-interval, son dos cosas diferentes. Otro tema es: si entiendo bien el chi-squared utiliza los errores, correcto? Noten que modifiqué a errores porcentuales (mucho más claro) tal como se describen en las conclusiones (los corregí un poco, aquí y allá), que los saqué de la Tabla 7, y re-escribí toda la frase (ver nuevo texto naranja), es correcta?. Ahora bien, son errores muy pequeños para cada celda, es poner demasiada fé en la tomografía :) Estos son los errores del valor mediano de $\Tm$. Podemos discutirlo, pero creo que los errores por punto (es decir, la $\Tm$ de cada voxel) deben adjudicarse valores mayores. Quizá esto de paso hace que el chi-squared ralee menos?}

{To determine if a traced filed line leg is of type up or down, we first determine the Pearson correlation coefficient $\rhoTr$ between the DEMT temperature $\Tm$ and the heliocentric height $r$ data points. We then select field lines for which the temperature increases or decreases significantly with height by requiring $|\rhoTr| > 0.5$. We then measure the quality of the linear fit to the temperature-height data by means of a chi-squared test \citep{recipes}, and select legs for which the fit has a 90\% confidence level. In this way, legs for which the DEMT temperature does not show a significant variation with height, or the linear fit to temperature is good enough, are not considered in this analysis. Finally, selected legs are then classified as up or down according to if $\rhoTr > +0.5$ or $\rhoTr < -0.5$, respectively. The linear fit allows characterization of the variation of $\Tm$ with height by means of a characteristic temperature gradient $\dr \Tm\,[\MK/\mrsun]$ along each leg. \albert{The chi-squared test to evaluate the quality of the fits considers the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$.} In summary, to be selected a leg must meet all three following conditions:}

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The condifence level of both the exponential and linear fits must be larger than 90\%.}
\end{enumerate}

{To characterize the global thermodynamic state of the inner solar corona in distinct magnetic structures, the DEMT and AWSoM results were traced along the magnetic field lines of the latter model. Based on the geometry and size of the loops, as well as on their thermodynamical properties, their legs were classified in four different types in this work:}

@@

In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown \albert{in Section \ref{demt_res}} below, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

{For both target rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations (\ref{Nfit})-(\ref{Tfit}). Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the \albert{$\approx 48000$} legs selected for CR-2082, 21\% are type 0, 31\% are type I, 22\% are type II and 26\% type III. On the other hand, of the \albert{$\approx 57000$} legs selected for CR-2208, 9\% are type 0, 36\% are type I, 26\% are type II and 29\% type III.

@@

In comparing the DEMT results obtained for the two selected targets, it is important to bear in mind they rely on data provided by two different instruments: AIA and EUVI. In order to quantify the systematic difference of the DEMT products based on both instruments, \citet{nuevo_2015}, who were the first to apply DEMT to AIA data, {analysed} a single target using both instruments independently. They found that while the density product is essentially equal, the temperature product of DEMT based on AIA data is systematically 8\% larger than the one based on EUVI data, i.e. $\Tm^{\rm(AIA)}/\Tm^{\rm(EUVI)} \approx 1.08$. Considering such correction, Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} indicate that CR-2208 was $\approx 10-15\%$ hotter than CR-2082 throughout the streamer belt region. As for the electron density products, CR-2208 was found to be $\approx 15-20\%$ less dense than CR-2082 throughout the streamer belt region. These systematic differences are beyond the uncertainty level in the DEMT products due to systematic sources (radiometric calibration and tomographic regularization), that \citet{lloveras_2017} \albert{estimated to be $\Delta\Tm\approx 6\%$ and $\Delta\sqravgN\approx 3\%$}.
